\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity in Human Brains}

### 2014-01-17 docs/paper/paper final.tex
legenda en labels bij assen toegevoegd in de verdelingsgrafieken

% Needed packages
\documentclass[a4paper, 10pt, english, onecolumn]{article}
\usepackage[english]{babel}
\usepackage[cm]{fullpage}
\usepackage{cite}
\usepackage{anysize}
\usepackage{setspace}
%\usepackage[compact]{titlesec}
\usepackage{graphicx}
\usepackage{stfloats}
\usepackage{listings}
\usepackage{hyperref}

\usepackage{amssymb,amsmath}
\usepackage{algorithmicx}
%\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

% for coloring individual cells in a table
\usepackage[table]{xcolor}
%\usepackage{pgfgantt}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=0.29\textheight]{images/new/struct_subj1-crop}
  \includegraphics[height=0.29\textheight]{images/new/struct_subj2_colorbar-crop} % one colorbar at the top right of the figure
  \includegraphics[height=0.29\textheight]{images/new/struct_subj3-crop}
  \includegraphics[height=0.29\textheight]{images/new/struct_subj4-crop}
  \includegraphics[height=0.29\textheight]{images/new/struct_subj5-crop}
  \includegraphics[height=0.29\textheight]{images/new/struct_subj6-crop}
  \caption{The structure of all six subjects as found with the PC algorithm. The two diagonal lines represent connections between the two hemispheres.}
\label{fig:struct_subjects}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.49\textwidth]{images/struct_full}
  \includegraphics[width=0.49\textwidth]{images/structure_max}
  \caption{The avarage structure of all subjects. The structure on the left is found with the PC-algorithm, and the structure on the right is found with DWI-measurements by Hinne et al. The two diagonal lines represent connections between the two hemispheres.}
\label{fig:struct_avg}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=0.26\textheight]{images/new/assym_subj1_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj2_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj3_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj4_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj5_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj6_expl-crop}
  \caption{The assymetric parts of the PDAG found with EMS-PC for all six subjects, in which a high value denotes a high certainty of a one-directional arrow.}
label{fig:asym_subjects}
\end{figure}

@@

To illustrate the difference in certainties between bi-directional and one-directional edges, the distributions of these values are presented in figure~\ref{fig:distributions}.
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.49\textwidth]{images/new/dist_all_mod_blackstruct_reddir_blueantisym-crop}
  \includegraphics[width=0.49\textwidth]{images/new/dist_all_expl_blackstruct_reddir_blueantisym-crop}
  \caption{The distribution of values, for standard PC at the left, and EMS-PC at the right. The horizontal axis shows the relative number of occurences in the graph. Zero-values make up more than 84\% of the graph, these are not shown in this distribution. The black line represent the distribution of results of the structural part of PC, and is equal for both variants. The red and the blue line represent the distribution of values of arrowheads and one-directional arrows, respectively.}
  \label{fig:distributions}
\end{figure}

>>>>

% Needed packages
\documentclass[a4paper, english]{article}
\usepackage[english]{babel}
%\usepackage[cm]{fullpage}
\usepackage{cite}
%\usepackage{anysize} <- this makes the article much wider
\usepackage{setspace}
%\usepackage[compact]{titlesec}
\usepackage{graphicx}
\usepackage{stfloats}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{amssymb,amsmath}
\usepackage{algorithmicx}
%\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
% for coloring individual cells in a table
\usepackage[table]{xcolor}
%\usepackage{pgfgantt}

@@

\begin{figure}[h!]
\hspace{-0.5in}
\begin{minipage}[t]{1.2\textwidth}
  \centering
  \includegraphics[height=0.29\textheight]{images/new/struct_subj1-crop}
  \includegraphics[height=0.29\textheight]{images/new/struct_subj2_colorbar-crop} % one colorbar at the top right of the figure
  \includegraphics[height=0.29\textheight]{images/new/struct_subj3-crop}
  \includegraphics[height=0.29\textheight]{images/new/struct_subj4-crop}
  \includegraphics[height=0.29\textheight]{images/new/struct_subj5-crop}
  \includegraphics[height=0.29\textheight]{images/new/struct_subj6-crop}
  \end{minipage}
\caption{The structure of all six subjects as found with the PC algorithm. The two diagonal lines represent connections between the two hemispheres.}

\label{fig:struct_subjects}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.49\textwidth]{images/struct_full}
  \includegraphics[width=0.49\textwidth]{images/structure_max}
  \caption{The avarage structure of all subjects. The structure on the left is found with the PC algorithm, and the structure on the right is found with DWI-measurements by Hinne et al. The two diagonal lines represent connections between the two hemispheres.}
\label{fig:struct_avg}
\end{figure}

@@

\begin{figure}[h!]
\hspace{-0.4in}
\begin{minipage}[t]{1.2\textwidth}
  \centering
  \includegraphics[height=0.26\textheight]{images/new/assym_subj1_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj2_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj3_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj4_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj5_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj6_expl-crop}
\end{minipage}
  \caption{The asymetric parts of the partial DAG found with EMS-PC for all six subjects, in which a high value denotes a high certainty of a one-directional arrow.}
\label{fig:asym_subjects}
\end{figure}

@@

To illustrate the difference in certainties between bi-directional and one-directional edges, the distributions of these values are presented in figure~\ref{fig:distributions}.
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.49\textwidth]{images/new/dist_all_mod_legend-crop}
  \includegraphics[width=0.49\textwidth]{images/new/dist_all_expl_legend-crop}
  \caption{The distribution of values, for standard PC at the left, and EMS-PC at the right. Zero-values make up more than 84\% of the graph, these are not shown in this distribution. The black line represent the distribution of results of the structural part of PC, and is equal for both variants. The red and the blue line represent the distribution of values of arrowheads and one-directional arrows, respectively.}
  \label{fig:distributions}
\end{figure}
